Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome

### 2023-05-31 paper/paper.qmd
Tweak risk threshold table

## Estimating the benefits of severity prediction models

@@

```{r risk_95th_pct_decision_thresholds, message=FALSE}
#| label: tbl-risk
#| tbl-cap: "**Predive model performance at 95th percentile of risk.**"
read_csv(here('results','decision_thresholds.csv')) %>% kable()
```

>>>>

## Estimating clinical benefit

@@

```{r risk_95th_pct_decision_thresholds, message=FALSE}
#| label: tbl-risk
#| tbl-cap: "**Predictive model performance at 95th percentile of risk.** The confusion matrix was computed at the 95th percentile of risk for each severity prediction model, which corresponds to 5% of cases predicted to be severe."
read_csv(here('results','decision_thresholds.csv')) %>% kable()
```
